OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-08-13 paper/paper.Rmd
Split datasets up to 90% reference fraction

For each dataset, a fraction of the sequences was selected to be clustered _de
novo_ into reference OTUs with OptiClust.
We used three methods for selecting the fraction of sequences to be used
as the reference: a simple random sample, weighting sequences by relative
abundance, and weighting by similarity to other sequences in the dataset.
Dataset splitting was repeated with reference fractions ranging from 10% to 80%
of the dataset and for 100 random seeds.
For each dataset split, the remaining sequences were assigned to the reference
OTUs with OptiFit.

>>>>

For each dataset, a fraction of the sequences was selected to be clustered _de
novo_ into reference OTUs with OptiClust.
We used three methods for selecting the fraction of sequences to be used
as the reference: a simple random sample, weighting sequences by relative
abundance, and weighting by similarity to other sequences in the dataset.
Dataset splitting was repeated with reference fractions ranging from 10% to 90%
of the dataset and for 100 random seeds.
For each dataset split, the remaining query sequences were assigned to the
reference OTUs with OptiFit.
